%education
\ecvitem{\highlight{Occupational field} }{\highlight{Research in applied and computational mathematics}}% desired job
\ecvitem{Responsibilities}
{-- Conducting research, publishing and presenting results of projects}
\ecvitem{}{-- Networking, securing funding and writing applications for grants}
\ecvitem{}{-- Software development in C\#, Python}

\ecvitem{Research interests}
{-- Multi-scale methods and homogenization for fluid flow}
\ecvitem{}{-- Inverse modelling and optimization} 
\ecvitem{}{-- Integration of real-time data with physical models}

% Last working experience
\ecvsection{Work Experience}
\ecvitemproj[
\begin{cvitemize}
%  \item Responsibilities:
% 
%  \item Projects:
%  \begin{cvitemize}
%TODO add Geosteering for IOR project leader
 \item Geosteering for IOR (Project leader since 2018)
 \subitem Development and implementation of closed loop ensemble-based geosteering workflow
 \subitem Global optimization of well trajectories under uncertainty
 \subitem Integration with industry tools for EM modelling and inversion
 \item Drilling Data Hub: a framework for data streaming and aggregation. \cite{suter2017rthub}
 \subitem Preparation of data  model suitable for drilling automation.
 \subitem Development of a complete prototype for reference server-client implementation.
 \subitem Demonstration of core functionality in real-time virtual environment. 
 \item PressureAhead: Reduced uncertainty in overpressures and drilling window prediction ahead of the bit (DrillWell). 
 \subitem Analysis of indirect measurement to predict overpressures and related uncertainties.
 %\subitem RT-Hub: drilling data acquisition and aggregation system. 
 \item Pre-project for CFD-based calculation and risk analysis for medical applications. \cite{alyaev2016elucidating}
 \item DrillScene. Improvement of usability of drilling monitoring system. (Sekal)
 \subitem Focus on automated trending and system calibration.
 \item Drilling solutions for improved recovery (DrillWell). \cite{luo2015ensemble}
 \subitem Development of a complete ensemble-based geosteering workflow
 \subitem Successful application for a follow-up project "Geosteering for IOR" (NFR 268122)
 \item Advanced drilling fluid processing. \cite{iversen2015towards}
 \subitem Development of simulator of top side processing equipment
 \subitem Modelling for drilling fluids processing advisory.
 \subitem Drilling fluid composition optimization
%  \end{cvitemize}
\end{cvitemize}
]
{2013 $\longrightarrow$}
{International Research Institute of Stavanger, Bergen, Norway.}
\ecvitemproj{
2010 -- 2013}{
PhD Research Fellow, University of Bergen, Norway.}
\ecvitemproj[
\begin{cvitemize}
\item Heuristics-based modeling of fracture generation and growth in oil reservoirs (C++).
\item 3D visualization of the modeling results.
\end{cvitemize}
]
{2009 -- 2010}
{Summer student, Statoil Research Center, Bergen, Norway.}
\ecvitemproj[
Investigation of databases for cloud computing. (Java)
]
{2008 -- 2008}
{Intern, Mirantis/Grid Dynamics, Saratov, Russia.}

% School

\ecvsection{Education and training}

\ecvitemproj[
\begin{cvitemize}
 \item Mathematical analysis of fractal structure formation in freezing brine. (Matlab) \cite{alyaev2017fractal}
 \item Semi-analytical solution for micro-mechanics of agglomeration forced by capillary bridging. (Maple) \cite{balakin2013micromechanics}
 \item Development and analysis of control volume HMM for non-linear flows in porous media. (Python) \cite{alyaev2014analysis},\cite{alyaev2012multiscale};
 with focus on near-well modeling \cite{alyaev2016multiscale}.
\end{cvitemize}
]
{2010 -- 2017}
{Ph.D., Applied Mathematics, University of Bergen, Norway. 
\ifdefined\disputationdate
  \highlight{Disputation date: \disputationdate}
\else
\fi
\cite{alyaev2016thesis}}
\ecvitemproj[
Credits: 150. Grade: A. \cite{alyaev2010adaptive}
]
{2008 -- 2010}
{M.Sc., Applied Mathematics, University of Bergen, Norway.}
\ecvitemproj[
With honors. Major in Mechanics of gas liquid and plasma. \cite{alyaev2008influence}
]
{2004 -- 2010}
{Specialist Diploma, Mechanics, Saratov State University, Russia.}

% Volunteer experiences

%\ecvsection{Volunteer Experience}