\providecommand{\urlprefix}{URL }
\ecvitem{\highlight{Publications}}{Journal Articles}
\paperecvitem{\label{alyaev2017fractal}Alyaev~S., Keilegavlen~E., Nordbotten~J.M., and Pop~I.S. (2017)}{\highlight{Fractal structures in freezing brine,} Journal of Fluid Mechanics. URL \url{http://dx.doi.org/10.1017/jfm.2017.472}}
\paperecvitem{\label{alyaev2014analysis}Alyaev~S., Keilegavlen~E., and Nordbotten~J.M. (2014)}{\highlight{Analysis of control volume heterogeneous multiscale methods for single phase flow in porous
media,} Multiscale Modeling \& Simulation. URL \url{http://hdl.handle.net/1956/15562}}
\paperecvitem{\label{balakin2013micromechanics}Balakin~B.V., Alyaev~S., Hoffmann~A.C., and Kosinski~P. (2013)}{\highlight{Micromechanics of agglomeration forced by the capillary bridge: the restitution of
momentum,} AIChE Journal. URL \url{http://dx.doi.org/10.1002/aic.14162}}
\ecvitem{\highlight{Other publications}}{}
\paperecvitem{\label{alyaev2018interactive}Alyaev~S., Bratvold~R.B., Luo~X. et~al. (2018)}{\highlight{An Interactive Decision Support System for Geosteering Operations,} in SPE Norway One Day Seminar. URL \url{http://dx.doi.org/10.2118/191337-MS}}
\paperecvitem{\label{suter2017rthub}Suter~E., Alyaev~S., and Daireaux~B. (2017)}{\highlight{{RT-Hub}: next generation real-time data aggregation while drilling,} in First EAGE Workshop on Pore Pressure Prediction. URL \url{http://dx.doi.org/10.3997/2214-4609.201700060}}
\paperecvitem{\label{alyaev2016multiscale}Alyaev~S., Keilegavlen~E., and Nordbotten~J.M. (2017)}{\highlight{Multiscale simulations of non-linear flows in porous media,} submitted to Computational geosciences. }
\paperecvitem{\label{alyaev2016elucidating}Alyaev~S., Bogdanova~A., Farbu~E.H., and Balakin~B.V. (2016)}{\highlight{Elucidating empty nose syndrome with CFD,} in VCBM \& MedViz. }
\paperecvitem{\label{alyaev2016thesis}Alyaev~S. (2016)}{\highlight{Multiscale analysis of selected problems in fluid dynamics,} PhD thesis. University of Bergen. URL \url{http://hdl.handle.net/1956/15563}}
\paperecvitem{\label{luo2015ensemble}Luo~X., Eliasson~P., Alyaev~S. et~al. (2015)}{\highlight{An Ensemble-Based Framework for Proactive Geosteering,} in SPWLA 56th Annual Logging Symposium. URL \url{http://www.onepetro.org/conference-paper/SPWLA-2015-KKKK}}
\paperecvitem{\label{iversen2015towards}Iversen~F., Daireaux~B., Alyaev~S. et~al. (2015)}{\highlight{Towards Closing the Loop on Drilling Fluid Management Control,} in SPE Bergen One Day Seminar. URL \url{http://dx.doi.org/10.2118/173887-MS}}
\paperecvitem{\label{alyaev2012multiscale}Alyaev~S., Keilegavlen~E., and Nordbotten~J.M. (2012)}{\highlight{Multiscale simulation of non-Darcy flows,} in Computational Methods in Water Resources, CMWR XIX. URL \url{http://hdl.handle.net/1956/15561}}
\paperecvitem{\label{alyaev2010adaptive}Alyaev~S. (2010)}{\highlight{Adaptive Multiscale Methods Based on A Posteriori Error Estimates,} Master's thesis. University of Bergen. URL \url{http://hdl.handle.net/1956/13151}}
\paperecvitem{\label{alyaev2008influence}Alyaev~S., and Antonenko~E.V. (2008)}{\highlight{Influence of non-uniformity of a thin-walled cylinder on axial critical forces,} Mathematics. Mechanics. (Collection of scientific papers). {In Russian}. }

